---
title: "Creating conservation-sensitive, climate-smart fisheries closures for the ABNJ of the Pacific Ocean"
output: 
  html_document:
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

We wish to create **conservation-sensitive**, **climate-smart** fisheries closures for the ABNJ of the Pacific Ocean using *prioritizr*.

*Prioritizr* (Hanson et al., 2018) is a spatial prioritization software (R package) that uses integer linear programming (ILP) allowing it to create exact solutions to large spatial planning problems faster than its heuristic counterparts (e.g. Marxan).

This file runs multiple scripts found in the main Github repository: [tinbuenafe/PacificProj](https://github.com/tinbuenafe/PacificProj), where the codes are explained in greater detail.

## Assembling the data layers

Before running *prioritizr*, we first had to assemble the following data layers:

1. Study Area
2. Fisheries conservation features
3. Climate smart features
4. Cost layer

```{r child = file.path("Chapter1.Rmd")}
```

\newpage

```{r child = file.path("Chapter2.Rmd")}
```

\newpage

```{r child = file.path("Chapter3.Rmd")}
```

\newpage

```{r child = file.path("Chapter4.Rmd")}
```

\newpage

```{r child = file.path("Chapter5.Rmd")}
```

\newpage

## Running prioritizr

*prioritizr* (v. 7.0.1.2) uses the following functions to define the `problem`.

```{r eval = FALSE, echo = TRUE}
# installing latest version of prioritizr from GitHub
devtools::install_github("prioritizr/prioritizr")
# installing gurobi as the optimizer
install.packages("/Library/gurobi911/mac64/R/gurobi_9.1-1_R_4.0.2.tgz", repos = NULL)
library(priortizr)
library(gurobi)

p1 <- prioritizr::problem(x, feature_list, "cost") %>% 
    add_min_set_objective() %>%
    add_relative_targets(target_list) %>%
    add_binary_decisions() %>%
    add_gurobi_solver(gap = 0.1, verbose = FALSE) 

s1 <- solve(p1)
```

  * `problem()`: we define the data
  * `x`: data frame having all the data layers (all planning units with their specific ID (`cellsID`), features data, cost)
  * `feature_list`: list of the features in `x`
  * `cost`: name of the column in `x` where the cost is found
  * `add_min_set_objective()`: function that allows us to employ the **minimum set objective function**. This allows *prioritizr* to create spatial plans that will minimize the cost.
  * `add_relative_targets()`: `target_list` list of assigned  targets for each feature
  * `add_binary_decisions()`: *prioritizr* will only either select or not select a PU
  * `add_gurobi_solver()`: Gurobi was used as the optimizer to solve the problem (at a default 10%)
  * `solve()`: *prioritizr* solves the problem `p1`
  
\newpage  

```{r child = file.path("Chapter6.Rmd")}
```

\newpage

```{r child = file.path("Chapter7.Rmd")}
```