---
title: "Summary"
output: html_document
---

## Summary

Since we ran *prioritizr* from 10 - 100% maximum target representation (in increments of 10%), we're showing a summary of how cost and percent protection varied with increasing target representation.

```{r eval = TRUE, echo = TRUE, message = FALSE, fig.height = 8, fig.width = 20, fig.align = 'center'}
source("scripts/12d_Stat_fCreateSummaryRuns.R")
# showing the log(cost), log(% area protected), number of protected planning units, and number of adequately represented features.
# this was done to determine which maximum representation targets to report/use in the runs
smart_plans
```

We also determined **Cohen's Kappa Coefficient** between plans created for each run. Below are the summaries for each run as well as a matrix plot of the correlations between plans. We also show the **summaries of the representation of each feature** for each spatial plan.

The relevant scripts for this part are found in `~/scripts/` with prefix `12_Stat`.
```{r eval = FALSE, echo = TRUE}
# the function for creating the correlation plots is found in:
source("scripts/12e_Stat_fKappaCorrplot.R")
# the runs are found in:
source("scripts/12f_Stat_fKappaCorrplotRun.R")

# the function for creating circular bar plots to show summaries of the representation of each feature:
source("scripts/12g_Stat_fCreateCircBarPlot.R")
# the runs are found in:
source("scripts/12h_Stat_fCreateCircBarPlotRuns.R")
```

**Summary for Run 2: Maximum Target = 90%**
```{r eval = TRUE, echo = FALSE, message = FALSE, fig.height = 5, fig.align = 'center', warning = FALSE}
library(tidyverse)
summary <- read_csv("outputs/12_Stat/12d_fCreateSummary/NoProv/IUCN_stat_summary.csv") %>% 
  filter(target == 90)
summary
```
```{r eval = TRUE, echo = FALSE, message = FALSE, results = FALSE, fig.height = 5, warning = FALSE, fig.align = 'center'}
source("scripts/12e_Stat_fKappaCorrplot.R")
corrplot <- fKappaCorrplot(inpdir = "outputs/12_Stat/12e_Kappa/run3/",
  name_cols = c("SSP1-2.6", "SSP2-4.5", "SSP5-8.5", "Uninformed"))
corrplot

```
```{r eval = TRUE, echo = FALSE, message = FALSE, results = FALSE, fig.height = 8, fig.width = 10, warning = FALSE, fig.align = 'center'}
source('scripts/12g_Stat_fCreateCircBarPlot.R')
circplot_target90 <- fCreateCircBarPlot(bycatch = 'bycatchIUCN',
                                        commercial = 'commercial',
                                        target_inpdir = 'outputs/09_Target/09d-e_TargetRuns/02_Target90/',
                                        features.summary_csv = 'outputs/12_Stat/12b_fSolutionSummary/NoProv/IUCN_features_rep_summary.csv',
                                        target = 'Target90')
circplot_target90 +
  theme(legend.position = 'right')
```

**Summary for Run 5: Maximum Target = 60%**
```{r eval = TRUE, echo = FALSE, message = FALSE, fig.height = 5, fig.align = 'center'}
library(tidyverse)
summary <- read_csv("outputs/12_Stat/12d_fCreateSummary/NoProv/IUCN_stat_summary.csv") %>% 
  filter(target == 60)
summary
```
```{r eval = TRUE, echo = FALSE, message = FALSE, results = FALSE, fig.height = 5, warning = FALSE, fig.align = 'center'}
source("scripts/12e_Stat_fKappaCorrplot.R")
corrplot <- fKappaCorrplot(inpdir = "outputs/12_Stat/12e_Kappa/run4/",
  name_cols = c("SSP1-2.6", "SSP2-4.5", "SSP5-8.5", "Uninformed"))
corrplot

```
``` {r eval = TRUE, echo = FALSE, message = FALSE, results = FALSE, fig.height = 8, fig.width = 10, warning = FALSE, fig.align = 'center'}
source("scripts/12g_Stat_fCreateCircBarPlot.R")
circplot_target60 <- fCreateCircBarPlot(bycatch = 'bycatchIUCN',
                                        commercial = 'commercial',
                                        target_inpdir = 'outputs/09_Target/09d-e_TargetRuns/05_Target60/',
                                        features.summary_csv = 'outputs/12_Stat/12b_fSolutionSummary/NoProv/IUCN_features_rep_summary.csv',
                                        target = 'Target60')
circplot_target60 +
  theme(legend.position = 'right')
```

**Summary for Run 8: Maximum Target = 30%**
```{r eval=TRUE, echo=FALSE, fig.align='center', fig.height=4, message=FALSE, warning=FALSE}
library(tidyverse)
summary <- read_csv("outputs/12_Stat/12d_fCreateSummary/NoProv/IUCN_stat_summary.csv") %>% 
  filter(target == 30)
summary
```
```{r eval = TRUE, echo = FALSE, message = FALSE, results = FALSE, fig.height = 5, warning = FALSE, fig.align = 'center'}
source("scripts/12e_Stat_fKappaCorrplot.R")
corrplot <- fKappaCorrplot(inpdir = "outputs/12_Stat/12e_Kappa/run5/",
  name_cols = c("SSP1-2.6", "SSP2-4.5", "SSP5-8.5", "Uninformed"))
corrplot
```
```{r eval = TRUE, echo = FALSE, message = FALSE, results = FALSE, fig.height = 8, fig.width = 10, warning = FALSE, fig.align = 'center'}
source("scripts/12g_Stat_fCreateCircBarPlot.R")
circplot_target30 <- fCreateCircBarPlot(bycatch = 'bycatchIUCN',
                                        commercial = 'commercial',
                                        target_inpdir = 'outputs/09_Target/09d-e_TargetRuns/08_Target30/',
                                        features.summary_csv = 'outputs/12_Stat/12b_fSolutionSummary/NoProv/IUCN_features_rep_summary.csv',
                                        target = 'Target30')
circplot_target30 + theme(legend.position = 'right')
```
