---
title: "Representation Targets"
output: html_document
---

## Representation targets

### Filtering and retaining PUs

We join the climate-smart layer with the conservation features layer. Then, we only retain planning units that have RCE and/or climate-velocity values belonging to their lower 25th percentile range. This was how we priortized protection of areas that are predicted to have *lower exposure to climate warming* and *higher retention of biodiversity*.

We used the function `fFilterQuartile()` and the scripts that are relevant for this step are found in `~/scripts/` with the prefix `08_Filter`.
``` {r eval = FALSE, echo = TRUE}
# function is found at:
source("scripts/08a_Filter_fFilterQuartile.R")
# function is ran at:
source("scripts/08d_Filter_fFilterQuartile25Run_NoProv.R")
```

This was done for both the bycatch and large pelagic layers, across different scenarios (SSP1-2.6, SSP2-4.5, SSP5-8.5). Below is an example of how the data looks like, with the following columns:

  * `cellsID`: unique ID for each PU
  * `species`: species code
  * `total_area`: the total area covered by each subtyped feature (in km$^{-1}$)
  * `velocity`: climate velocity
  * `velo_tvalue`: transformed values of climate velocity (velocity * 10)
  * `RCE`: RCE index values
  * `RCE_tvalue`: transformed values of RCE (cube root of RCE)

```{r eval = TRUE, echo = FALSE, message = FALSE}
library(sf)
library(tidyverse)
```
```{r eval = TRUE, echo = TRUE, message = FALSE, warning = FALSE}
# for bycatch under the climate scenario SSP1-2.6.
bycatchSSP126 <- readRDS("outputs/08_Filter/08d_Filter25_NoProv/bycatchIUCNSSP126_25percentile.rds") %>% 
  as_tibble() %>% 
  dplyr::select(-area_km2, -cellsID.2, -geometry)
head(bycatchSSP126)
# for large pelagics under the cliamte scenario SSP5-8.5.
commercialSSP585 <- readRDS("outputs/08_Filter/08d_Filter25_NoProv/commercialSSP585_25percentile.rds") %>% 
  as_tibble() %>% 
  dplyr::select(-area_km2, -cellsID.2, -geometry)
head(commercialSSP585)
```

Aside from these **climate-smart** closures, we also explored **climate-uninformed**, wherein the climate-smart features were not included in the analyses. Subsequently, the step of filtering and retention of planning units was also not included.
```{r eval = FALSE, echo = TRUE}
source("scripts/08e_Filter_fFilterQuartile100Run_NoProv.R")
```

This is how the data looks like:
```{r eval = TRUE, echo = FALSE, message = FALSE}
library(sf)
library(tidyverse)
```
```{r eval = TRUE, echo = TRUE, message = FALSE, warning = FALSE}
# for bycatch:
bycatch_uninformed <- readRDS("outputs/08_Filter/08e_Filter100_NoProv/bycatchIUCNuninformed_100percentile.rds") %>% 
  as_tibble() %>% 
  dplyr::select(-area_km2, -geometry)
head(bycatch_uninformed)
# for large pelagics:
commercial_uninformed <- readRDS("outputs/08_Filter/08e_Filter100_NoProv/commercialuninformed_100percentile.rds") %>%
  as_tibble() %>% 
  dplyr::select(-area_km2, -geometry)
head(commercial_uninformed)
```

### Assigning targets

To determine the *relative targets* per subtyped feature, we checked each one's *IUCN category* (IUCN, 2015) using `rredlist()`. Threatened features (i.e. classified as vulnerable, endangered, threatened) were assigned a *fixed maximum target*. Features ($i$) that were not classified as threatened (e.g. classified as near-threatened, etc.) were assigned a *relative target* based on their distribution.

  Relative target$_i$ $= Target_{max} \cdot \frac{PU_i}{PU_{total}} \cdot (Target_{max} - Target_{min})$
  
  * `PU_i`: number of planning units of feature $i$
  * `PU_{total}`: total number of planning units in planning region
  * `Target_{max}`: Maximum target / the fixed maximum target assigned to threatened features (e.g. 1)
  * `Target_{min}`: Minimum target (e.g. 0.1)
  
Lower targets are assigned to features with broader distribution, and higher targets to features with more restricted distribution.

We reran this step for an array of targets, for both climate-smart and climate-uninformed closures:

``` {r echo = FALSE, results = 'asis', message = FALSE}
library(knitr)
library(tidyverse)
library(kableExtra)
run <- c("1", "2", "3", "4", "5", "6", "7", "8", "9", "10")
max <- c(1, 0.9, 0.8, 0.7, 0.6, 0.5, 0.4, 0.3, 0.2, 0.1)
min <- c(0.1, 0.1, 0.1 , 0.1, 0.1, 0.1, 0.1, 0.1, 0.1, 0)
df <- cbind(run, max, min)
colnames(df) <- c("Runs", "Maximum","Minimum")
kable(df) %>% 
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
```

We used the function `fRepresentTarget()`, and the scripts are found in `~/scripts/` with the prefix `09`.
```{r eval = FALSE, echo = TRUE}
# the function is found in:
source("scripts/09a_Target_fRepresentTarget.R")
# the runs for climate-smart closures are found in:
source("scripts/09d_Target_fRepresentTargetSmartRun_NoProv.R")
# the runs for climate-uninformed closures are found in:
source("scripts/09e_Target_fRepresentTargetUninformedRun_NoProv.R")
```

For this `.rmd`, we'll be showing results using **Runs 2** (Max = 0.9, Min = 0.1), **5** (Max = 0.6, Min = 0.1) and **8** (Max = 0.3, Min = 0.1). This workflow shows that it can be replicated using other parameters.

Below is an example of how the data looks like:
```{r eval = TRUE, echo = TRUE, message = FALSE}
target90_commercial <- readRDS("outputs/09_Target/09d-e_TargetRuns/02_Target90/SSP126/target_commercialSSP126.rds") %>% 
  as_tibble()
head(target90_commercial)
target90_bycatch <- readRDS("outputs/09_Target/09d-e_TargetRuns/02_Target90/SSP126/target_bycatchSSP126.rds") %>% 
  as_tibble()
head(target90_bycatch)
```

  * `new_features`: features
  * `total_area`: the total area covered by each subtyped feature (in km$^{-1}$)
  * `category`: IUCN redlist category
  * `target`: assigned target in percentage
