---
title: "Prioritizr Runs"
output: html_document
---

### Prioritizr Runs

We used the `fPrioritizrRun()` function to streamline the runs. `fPrioritizrRun()` arranges all the data and makes sure that they're in the right format, then runs `problem()` and `solve()`. This function also saves the summaries each plan (cost, % area protected and number of representative features that achieved 30% or more protection). 

The relevant scripts for this step is found in `~/scripts/` with the prefix `10`.
```{r eval = FALSE, echo = TRUE}
# the function is in:
source("scrpits/10a_Prioritizr_fPrioritizr.R")
# to run the function with climate-smart data
source("scripts/10b_Prioritizr_fPrioritizrAQMSmartRun.R")
# to run the function with climate-uninformed data
source("scripts/10d_Prioritizr_fPrioritizrAQMUninformedRun.R")
# to create no-regret closures with the climate-smart plans
```

To create no-regret plans, we used thre function `fCreateNoRegret()` which intersected the selected PUs in all three climate scenarios. The relevant scripts for this step is found in `~/scripts` with the prefix `11`.
```{r eval = FALSE, echo = TRUE}
# the function is in:
source("scripts/11a_NoRegret_fCreateNoRegret.R")
# the runs are found in:
source("scripts/11b_NoRegret_fCreateNoRegretAQMRuns.R")
```

As mentioned in the previous section, we will only be showing results of **Runs 2** (Max = 0.9, Min = 0.1), **5** (Max = 0.6, Min = 0.1) and **8** (Max = 0.3, Min = 0.1).

### Run 2: Maximum Target = 90%

#### Climate-smart runs

**SSP1-2.6 run**
```{r eval = TRUE, echo = TRUE, message = FALSE, warning = FALSE}
SSP126_target90 <- readRDS("outputs/10_Prioritizr/10b-c_AQMRuns/02_Target90/solution_SSP126.rds")
```
```{r eval = TRUE, echo = FALSE, message = FALSE, fig.align = 'center'}
# defining generalities for plotting
library(tidyverse)
library(RColorBrewer)
library(patchwork)
pal_rich <- c("FALSE" = "lightsteelblue2", "TRUE" = "sienna3")
solution <- c("Not selected PUs", "Selected PUs")
world_sf <- readRDS("outputs/01_StudyArea/01a_StudyArea/PacificCenterLand.rds")
source("scripts/study_area/fCreateRobinsonBoundary.R")
Bndry <- fCreateRobinsonBoundary(west = 78, east = 140, north = 51, south = 60)
# plotting
ggplot() + 
  geom_sf(data = SSP126_target90, aes(fill = solution_1), color = "grey64", size = 0.02) +
  scale_fill_manual(name = "Solution",
                    values = pal_rich,
                    labels = solution) +
  geom_sf(data = world_sf, size = 0.05, fill = "grey20") +
  coord_sf(xlim = c(st_bbox(Bndry)$xmin, st_bbox(Bndry)$xmax), 
           ylim = c(st_bbox(Bndry)$ymin, st_bbox(Bndry)$ymax),
           expand = TRUE) +
  ggtitle("SSP 1-2.6") +
  theme_bw()
```

  * `cost` is in USD
  * `perc_area_protected` is the percentage of the Pacific ABNJ protected
  * `protected_PU` is the number of features that have >= 30% (by area) protection
```{r eval = TRUE, echo = FALSE, message = FALSE}
summary <- read_csv("statistics/stats.csv") %>% 
  filter(target == 90) %>% 
  filter(scenario == "SSP1.26")
summary
```

**SSP2-4.5 run**
```{r eval = TRUE, echo = TRUE, message = FALSE, warning = FALSE}
SSP245_target90 <- readRDS("outputs/10_Prioritizr/10b-c_AQMRuns/02_Target90/solution_SSP245.rds")
```
```{r eval = TRUE, echo = FALSE, message = FALSE, fig.align = 'center'}
ggplot() + 
  geom_sf(data = SSP245_target90, aes(fill = solution_1), color = "grey64", size = 0.02) +
  scale_fill_manual(name = "Solution",
                    values = pal_rich,
                    labels = solution) +
  geom_sf(data = world_sf, size = 0.05, fill = "grey20") +
  coord_sf(xlim = c(st_bbox(Bndry)$xmin, st_bbox(Bndry)$xmax), 
           ylim = c(st_bbox(Bndry)$ymin, st_bbox(Bndry)$ymax),
           expand = TRUE) +
  ggtitle("SSP 2-4.5") +
  theme_bw()
```

  * `cost` is in USD
  * `perc_area_protected` is the percentage of the Pacific ABNJ protected
  * `protected_PU` is the number of features that have >= 30% (by area) protection
```{r eval = TRUE, echo = FALSE, message = FALSE}
summary <- read_csv("statistics/stats.csv") %>% 
  filter(target == 90) %>% 
  filter(scenario == "SSP2.45")
summary
```

**SSP5-8.5 run**
```{r eval = TRUE, echo = TRUE, message = FALSE, warning = FALSE}
SSP585_target90 <- readRDS("outputs/10_Prioritizr/10b-c_AQMRuns/02_Target90/solution_SSP585.rds")
```
```{r eval = TRUE, echo = FALSE, message = FALSE, fig.align = 'center'}
ggplot() + 
  geom_sf(data = SSP585_target90, aes(fill = solution_1), color = "grey64", size = 0.02) +
  scale_fill_manual(name = "Solution",
                    values = pal_rich,
                    labels = solution) +
  geom_sf(data = world_sf, size = 0.05, fill = "grey20") +
  coord_sf(xlim = c(st_bbox(Bndry)$xmin, st_bbox(Bndry)$xmax), 
           ylim = c(st_bbox(Bndry)$ymin, st_bbox(Bndry)$ymax),
           expand = TRUE) +
  ggtitle("SSP 5-8.5") +
  theme_bw()
```

  * `cost` is in USD
  * `perc_area_protected` is the percentage of the Pacific ABNJ protected
  * `protected_PU` is the number of features that have >= 30% (by area) protection
```{r eval = TRUE, echo = FALSE, message = FALSE}
summary <- read_csv("statistics/stats.csv") %>% 
  filter(target == 90) %>% 
  filter(scenario == "SSP5.85")
summary
```

#### No-regret plan
```{r eval = TRUE, echo = TRUE, message = FALSE, warning = FALSE}
noregret_target90 <- readRDS("outputs/11_NoRegret/11b_AQMRuns/noregretclosures_Target90.rds")
```
```{r eval = TRUE, echo = FALSE, message = FALSE, fig.align = 'center'}
ggplot() + 
  geom_sf(data = noregret_target90, aes(fill = solution_1), color = "grey64", size = 0.02) +
  scale_fill_manual(name = "Solution",
                    values = pal_rich,
                    labels = solution) +
  geom_sf(data = world_sf, size = 0.05, fill = "grey20") +
  coord_sf(xlim = c(st_bbox(Bndry)$xmin, st_bbox(Bndry)$xmax), 
           ylim = c(st_bbox(Bndry)$ymin, st_bbox(Bndry)$ymax),
           expand = TRUE) +
  ggtitle("No-regret Plan") +
  theme_bw()
```

#### Climate-uninformed run
```{r eval = TRUE, echo = TRUE, message = FALSE, warning = FALSE}
uninformed_target90 <- readRDS("outputs/10_Prioritizr/10b-c_AQMRuns/02_Target90/solution_uninformed.rds")
```
```{r eval = TRUE, echo = FALSE, message = FALSE, fig.align = 'center'}
ggplot() + 
  geom_sf(data = uninformed_target90, aes(fill = solution_1), color = "grey64", size = 0.02) +
  scale_fill_manual(name = "Solution",
                    values = pal_rich,
                    labels = solution) +
  geom_sf(data = world_sf, size = 0.05, fill = "grey20") +
  coord_sf(xlim = c(st_bbox(Bndry)$xmin, st_bbox(Bndry)$xmax), 
           ylim = c(st_bbox(Bndry)$ymin, st_bbox(Bndry)$ymax),
           expand = TRUE) +
  ggtitle("Climate-Uninformed Plan") +
  theme_bw()
```

  * `cost` is in USD
  * `perc_area_protected` is the percentage of the Pacific ABNJ protected
  * `protected_PU` is the number of features that have >= 30% (by area) protection
```{r eval = TRUE, echo = FALSE, message = FALSE}
summary <- read_csv("statistics/stats.csv") %>% 
  filter(target == 90) %>% 
  filter(scenario == "uninformed")
summary
```

### Run 5: Maximum Target = 60%

#### Climate-smart runs

**SSP1-2.6 run**
```{r eval = TRUE, echo = TRUE, message = FALSE, warning = FALSE}
SSP126_target60 <- readRDS("outputs/10_Prioritizr/10b-c_AQMRuns/05_Target60/solution_SSP126.rds")
```
```{r eval = TRUE, echo = FALSE, message = FALSE, fig.align = 'center'}
ggplot() + 
  geom_sf(data = SSP126_target60, aes(fill = solution_1), color = "grey64", size = 0.02) +
  scale_fill_manual(name = "Solution",
                    values = pal_rich,
                    labels = solution) +
  geom_sf(data = world_sf, size = 0.05, fill = "grey20") +
  coord_sf(xlim = c(st_bbox(Bndry)$xmin, st_bbox(Bndry)$xmax), 
           ylim = c(st_bbox(Bndry)$ymin, st_bbox(Bndry)$ymax),
           expand = TRUE) +
  ggtitle("SSP 1-2.6") +
  theme_bw()
```

  * `cost` is in USD
  * `perc_area_protected` is the percentage of the Pacific ABNJ protected
  * `protected_PU` is the number of features that have >= 30% (by area) protection
```{r eval = TRUE, echo = FALSE, message = FALSE}
summary <- read_csv("statistics/stats.csv") %>% 
  filter(target == 60) %>% 
  filter(scenario == "SSP1.26")
summary
```

**SSP2-4.5 run**
```{r eval = TRUE, echo = TRUE, message = FALSE, warning = FALSE}
SSP245_target60 <- readRDS("outputs/10_Prioritizr/10b-c_AQMRuns/05_Target60/solution_SSP245.rds")
```
```{r eval = TRUE, echo = FALSE, message = FALSE, fig.align = 'center'}
ggplot() + 
  geom_sf(data = SSP245_target60, aes(fill = solution_1), color = "grey64", size = 0.02) +
  scale_fill_manual(name = "Solution",
                    values = pal_rich,
                    labels = solution) +
  geom_sf(data = world_sf, size = 0.05, fill = "grey20") +
  coord_sf(xlim = c(st_bbox(Bndry)$xmin, st_bbox(Bndry)$xmax), 
           ylim = c(st_bbox(Bndry)$ymin, st_bbox(Bndry)$ymax),
           expand = TRUE) +
  ggtitle("SSP 2-4.5") +
  theme_bw()
```

  * `cost` is in USD
  * `perc_area_protected` is the percentage of the Pacific ABNJ protected
  * `protected_PU` is the number of features that have >= 30% (by area) protection
```{r eval = TRUE, echo = FALSE, message = FALSE}
summary <- read_csv("statistics/stats.csv") %>% 
  filter(target == 60) %>% 
  filter(scenario == "SSP2.45")
summary
```

**SSP5-8.5 run**
```{r eval = TRUE, echo = TRUE, message = FALSE, warning = FALSE}
SSP585_target60 <- readRDS("outputs/10_Prioritizr/10b-c_AQMRuns/05_Target60/solution_SSP585.rds")
```
```{r eval = TRUE, echo = FALSE, message = FALSE, fig.align = 'center'}
ggplot() + 
  geom_sf(data = SSP585_target60, aes(fill = solution_1), color = "grey64", size = 0.02) +
  scale_fill_manual(name = "Solution",
                    values = pal_rich,
                    labels = solution) +
  geom_sf(data = world_sf, size = 0.05, fill = "grey20") +
  coord_sf(xlim = c(st_bbox(Bndry)$xmin, st_bbox(Bndry)$xmax), 
           ylim = c(st_bbox(Bndry)$ymin, st_bbox(Bndry)$ymax),
           expand = TRUE) +
  ggtitle("SSP 5-8.5") +
  theme_bw()
```

  * `cost` is in USD
  * `perc_area_protected` is the percentage of the Pacific ABNJ protected
  * `protected_PU` is the number of features that have >= 30% (by area) protection
```{r eval = TRUE, echo = FALSE, message = FALSE}
summary <- read_csv("statistics/stats.csv") %>% 
  filter(target == 60) %>% 
  filter(scenario == "SSP5.85")
summary
```

#### No-regret plan
```{r eval = TRUE, echo = TRUE, message = FALSE, warning = FALSE}
noregret_target60 <- readRDS("outputs/11_NoRegret/11b_AQMRuns/noregretclosures_Target60.rds")
```
```{r eval = TRUE, echo = FALSE, message = FALSE, fig.align = 'center'}
ggplot() + 
  geom_sf(data = noregret_target60, aes(fill = solution_1), color = "grey64", size = 0.02) +
  scale_fill_manual(name = "Solution",
                    values = pal_rich,
                    labels = solution) +
  geom_sf(data = world_sf, size = 0.05, fill = "grey20") +
  coord_sf(xlim = c(st_bbox(Bndry)$xmin, st_bbox(Bndry)$xmax), 
           ylim = c(st_bbox(Bndry)$ymin, st_bbox(Bndry)$ymax),
           expand = TRUE) +
  ggtitle("No-regret Plan") +
  theme_bw()
```

#### Climate-uninformed run
```{r eval = TRUE, echo = TRUE, message = FALSE, warning = FALSE}
uninformed_target60 <- readRDS("outputs/10_Prioritizr/10b-c_AQMRuns/05_Target60/solution_uninformed.rds")
```
```{r eval = TRUE, echo = FALSE, message = FALSE, fig.align = 'center'}
ggplot() + 
  geom_sf(data = uninformed_target60, aes(fill = solution_1), color = "grey64", size = 0.02) +
  scale_fill_manual(name = "Solution",
                    values = pal_rich,
                    labels = solution) +
  geom_sf(data = world_sf, size = 0.05, fill = "grey20") +
  coord_sf(xlim = c(st_bbox(Bndry)$xmin, st_bbox(Bndry)$xmax), 
           ylim = c(st_bbox(Bndry)$ymin, st_bbox(Bndry)$ymax),
           expand = TRUE) +
  ggtitle("Climate-Uninformed Plan") +
  theme_bw()
```

  * `cost` is in USD
  * `perc_area_protected` is the percentage of the Pacific ABNJ protected
  * `protected_PU` is the number of features that have >= 30% (by area) protection
```{r eval = TRUE, echo = FALSE, message = FALSE}
summary <- read_csv("statistics/stats.csv") %>% 
  filter(target == 60) %>% 
  filter(scenario == "uninformed")
summary
```

### Run 8: Maximum Target = 30%

#### Climate-smart runs

**SSP1-2.6 run**
```{r eval = TRUE, echo = TRUE, message = FALSE, warning = FALSE}
SSP126_target30 <- readRDS("outputs/10_Prioritizr/10b-c_AQMRuns/08_Target30/solution_SSP126.rds")
```
```{r eval = TRUE, echo = FALSE, message = FALSE, fig.align = 'center'}
ggplot() + 
  geom_sf(data = SSP126_target30, aes(fill = solution_1), color = "grey64", size = 0.02) +
  scale_fill_manual(name = "Solution",
                    values = pal_rich,
                    labels = solution) +
  geom_sf(data = world_sf, size = 0.05, fill = "grey20") +
  coord_sf(xlim = c(st_bbox(Bndry)$xmin, st_bbox(Bndry)$xmax), 
           ylim = c(st_bbox(Bndry)$ymin, st_bbox(Bndry)$ymax),
           expand = TRUE) +
  ggtitle("SSP 1-2.6") +
  theme_bw()
```

  * `cost` is in USD
  * `perc_area_protected` is the percentage of the Pacific ABNJ protected
  * `protected_PU` is the number of features that have >= 30% (by area) protection
```{r eval = TRUE, echo = FALSE, message = FALSE}
summary <- read_csv("statistics/stats.csv") %>% 
  filter(target == 30) %>% 
  filter(scenario == "SSP1.26")
summary
```

**SSP2-4.5 run**
```{r eval = TRUE, echo = TRUE, message = FALSE, warning = FALSE}
SSP245_target30 <- readRDS("outputs/10_Prioritizr/10b-c_AQMRuns/08_Target30/solution_SSP245.rds")
```
```{r eval = TRUE, echo = FALSE, message = FALSE, fig.align = 'center'}
ggplot() + 
  geom_sf(data = SSP245_target30, aes(fill = solution_1), color = "grey64", size = 0.02) +
  scale_fill_manual(name = "Solution",
                    values = pal_rich,
                    labels = solution) +
  geom_sf(data = world_sf, size = 0.05, fill = "grey20") +
  coord_sf(xlim = c(st_bbox(Bndry)$xmin, st_bbox(Bndry)$xmax), 
           ylim = c(st_bbox(Bndry)$ymin, st_bbox(Bndry)$ymax),
           expand = TRUE) +
  ggtitle("SSP 2-4.5") +
  theme_bw()
```

  * `cost` is in USD
  * `perc_area_protected` is the percentage of the Pacific ABNJ protected
  * `protected_PU` is the number of features that have >= 30% (by area) protection
```{r eval = TRUE, echo = FALSE, message = FALSE}
summary <- read_csv("statistics/stats.csv") %>% 
  filter(target == 30) %>% 
  filter(scenario == "SSP2.45")
summary
```

**SSP5-8.5 run**
```{r eval = TRUE, echo = TRUE, message = FALSE, warning = FALSE}
SSP585_target30 <- readRDS("outputs/10_Prioritizr/10b-c_AQMRuns/08_Target30/solution_SSP585.rds")
```
```{r eval = TRUE, echo = FALSE, message = FALSE, fig.align = 'center'}
ggplot() + 
  geom_sf(data = SSP585_target30, aes(fill = solution_1), color = "grey64", size = 0.02) +
  scale_fill_manual(name = "Solution",
                    values = pal_rich,
                    labels = solution) +
  geom_sf(data = world_sf, size = 0.05, fill = "grey20") +
  coord_sf(xlim = c(st_bbox(Bndry)$xmin, st_bbox(Bndry)$xmax), 
           ylim = c(st_bbox(Bndry)$ymin, st_bbox(Bndry)$ymax),
           expand = TRUE) +
  ggtitle("SSP 5-8.5") +
  theme_bw()
```

  * `cost` is in USD
  * `perc_area_protected` is the percentage of the Pacific ABNJ protected
  * `protected_PU` is the number of features that have >= 30% (by area) protection
```{r eval = TRUE, echo = FALSE, message = FALSE}
summary <- read_csv("statistics/stats.csv") %>% 
  filter(target == 30) %>% 
  filter(scenario == "SSP5.85")
summary
```

#### No-regret plan
```{r eval = TRUE, echo = TRUE, message = FALSE, warning = FALSE}
noregret_target60 <- readRDS("outputs/11_NoRegret/11b_AQMRuns/noregretclosures_Target60.rds")
```
```{r eval = TRUE, echo = FALSE, message = FALSE, fig.align = 'center'}
ggplot() + 
  geom_sf(data = noregret_target60, aes(fill = solution_1), color = "grey64", size = 0.02) +
  scale_fill_manual(name = "Solution",
                    values = pal_rich,
                    labels = solution) +
  geom_sf(data = world_sf, size = 0.05, fill = "grey20") +
  coord_sf(xlim = c(st_bbox(Bndry)$xmin, st_bbox(Bndry)$xmax), 
           ylim = c(st_bbox(Bndry)$ymin, st_bbox(Bndry)$ymax),
           expand = TRUE) +
  ggtitle("No-regret Plan") +
  theme_bw()
```

#### Climate-uninformed run
```{r eval = TRUE, echo = TRUE, message = FALSE, warning = FALSE}
uninformed_target30 <- readRDS("outputs/10_Prioritizr/10b-c_AQMRuns/08_Target30/solution_uninformed.rds")
```
```{r eval = TRUE, echo = FALSE, message = FALSE, fig.align = 'center'}
ggplot() + 
  geom_sf(data = uninformed_target30, aes(fill = solution_1), color = "grey64", size = 0.02) +
  scale_fill_manual(name = "Solution",
                    values = pal_rich,
                    labels = solution) +
  geom_sf(data = world_sf, size = 0.05, fill = "grey20") +
  coord_sf(xlim = c(st_bbox(Bndry)$xmin, st_bbox(Bndry)$xmax), 
           ylim = c(st_bbox(Bndry)$ymin, st_bbox(Bndry)$ymax),
           expand = TRUE) +
  ggtitle("Climate-Uninformed Plan") +
  theme_bw()
```

  * `cost` is in USD
  * `perc_area_protected` is the percentage of the Pacific ABNJ protected
  * `protected_PU` is the number of features that have >= 30% (by area) protection
```{r eval = TRUE, echo = FALSE, message = FALSE}
summary <- read_csv("statistics/stats.csv") %>% 
  filter(target == 30) %>% 
  filter(scenario == "uninformed")
summary
```