---
title: "Study Area"
output: html_document
---

### Study Area

The study area has the following characteristics:

* Pacific ABNJ
* Limited boundaries to areal jurisdiction of RFMOs responsible for managing large pelagic fisheries (IATTC and WCPFC)
* Robinson projection
* Divided into Longhurst provinces

We ran the following code using polygons from `rnaturalearth` package and the EEZ `.shp` files from Marine Regions (Flanders Marine Institute, 2019) to create a Pacific-centered map of the global ABNJs.

The relevant scripts for creating the study area are labeled with a prefix of `01` in `~/scripts/`.
```{r, eval = FALSE, echo = TRUE}
# to create the Pacific-centered maps:
source("scripts/01a_StudyArea_CreatingPUs.R")
# this script uses the following functions (embedded actual script):

# function to create polygon of the ABNJ by masking the EEZs and the landmasses
source("scripts/study_area/fCreateMaskedPolygon.R") 
# function to reproject these polygon to Robinson projection
source("scripts/study_area/fConvert2PacificRobinson.R") 
# function to create the hexagonal planning units
source("scripts/study_area/fCreate_PlanningUnits.R") 
```
``` {r, eval = TRUE, echo = FALSE, error = FALSE, warning = FALSE, message = FALSE, results = FALSE}
library(tidyverse)
source("scripts/study_area/fCreateRobinsonBoundary.R")
```
This figure shows the Pacific-centered global map (using Robinson projection).
```{r, eval = TRUE, echo = TRUE, error = FALSE, warning = FALSE, message = FALSE, results = FALSE, fig.height=3, fig.align = 'center'}
world_robinson <- readRDS("outputs/01_StudyArea/01a_StudyArea/PacificCenterLand.rds")
global_plot <- ggplot() +
  geom_sf(data = world_robinson, colour = "grey20", fill="grey20", size = 0.1, show.legend = "line") +
  theme_bw()
global_plot
```

We then created equal-area hexagonal planning units, or PUs, (0.5$^\circ$ x 0.5$^\circ$ at the equator) of the study area. This resulted in 31,917 PUs.
```{r, eval = TRUE, echo = TRUE, error = FALSE, warning = FALSE, message = FALSE, results = FALSE, fig.align = 'center'}
# define objects for plotting; objects are the result of running 01_StudyArea
pacific_robinson <- readRDS("outputs/01_StudyArea/01a_StudyArea/PacificCenterABNJ.rds")
PUsPac <- readRDS("outputs/01_StudyArea/01a_StudyArea/PacificABNJGrid_05deg.rds")
Bndry <- fCreateRobinsonBoundary(west = 78, east = 140, north = 51, south = 60) # coordinates in degrees

study_area <- ggplot() +
    geom_sf(data = pacific_robinson, colour = NA, fill = NA, size = 0.2, show.legend = "line") +
    geom_sf(data = world_robinson, color = "grey20", fill="grey20", size = 0.1, show.legend = "line") +
    geom_sf(data = PUsPac, colour = "grey64", aes(fill = "ABNJ"), size = 0.1, show.legend = TRUE) + 
    scale_fill_manual(name = "Study Area", values = c("ABNJ" = "coral3")) +
    coord_sf(xlim = c(st_bbox(Bndry)$xmin, st_bbox(Bndry)$xmax), # Set limits based on Bndry bbox
            ylim = c(st_bbox(Bndry)$ymin, st_bbox(Bndry)$ymax),
            expand = TRUE) +
    theme_bw()
study_area
```

After demarcating the study area, we categorized the PUs into their Longhurst Provinces, `.shp` files from Marine Regions (Flanders Marine Institute, 2009), using the function `fCategProv()` found in this source code.
```{r, eval = FALSE, echo = TRUE}
# function to assign the provinces defined in:
source("scripts/01b_StudyArea_fCategProv.R")
# running this function:
source("scripts/01c_StudyArea_fCategProvRun.R")
longhurst
```
```{r, eval = TRUE, echo = FALSE, error = FALSE, warning = FALSE, message = FALSE, results = FALSE, fig.align = 'center'}
source("scripts/01c_StudyArea_fCategProvRun.R")
longhurst
```
