---
title: "Summary"
output: html_document
---

## Summary

Since we ran *prioritizr* from 10 - 100% maximum target representation (in increments of 10%), we're showing a summary of how cost and percent protection varied with increasing target representation.

```{r eval = TRUE, echo = TRUE, message = FALSE, fig.height = 3, fig.align = 'center'}
source("scripts/12c_Stat_SomeAnalyses.R")
# log-transformed cost with increasing target representation:
log_plot
# % area protected with increasing target representation:
area_plot
# number of planning units that achieved 30% or more protection (maximum is 66)
protected_features
```

We also determined **Cohen's Kappa Coefficient** between plans created for each run. Below are the summaries for each run as well as a matrix plot of the correlations between plans.

The relevant scripts for this part are found in `~/scripts/` with prefix `12`.
```{r eval = FALSE, echo = TRUE}
# the function for creating the correlation plots is found in:
source("scripts/12d_Stat_fKappaCorrplot.R")
# the runs are found in:
source("scripts/12e_Stat_fKappaCorrplotRun.R")
```

**Summary for Run 2: Maximum Target = 90%**
```{r eval = TRUE, echo = FALSE, message = FALSE, fig.height = 5, fig.align = 'center'}
library(tidyverse)
summary <- read_csv("statistics/stats.csv") %>% 
  filter(target == 90)
summary
```
```{r eval = TRUE, echo = FALSE, message = FALSE, results = FALSE, fig.height = 4}
source("scripts/12d_Stat_fKappaCorrplot.R")
fKappaCorrplot(inpdir = "outputs/12_Stat/12e_Kappa/run3/",
  name_cols = c("SSP1-2.6", "SSP2-4.5", "SSP5-8.5", "Uninformed"))
```

**Summary for Run 5: Maximum Target = 60%**
```{r eval = TRUE, echo = FALSE, message = FALSE, fig.height = 5, fig.align = 'center'}
library(tidyverse)
summary <- read_csv("statistics/stats.csv") %>% 
  filter(target == 60)
summary
```
```{r eval = TRUE, echo = FALSE, message = FALSE, results = FALSE, fig.height = 4}
source("scripts/12d_Stat_fKappaCorrplot.R")
fKappaCorrplot(inpdir = "outputs/12_Stat/12e_Kappa/run4/",
  name_cols = c("SSP1-2.6", "SSP2-4.5", "SSP5-8.5", "Uninformed"))
```

**Summary for Run 8: Maximum Target = 30%**
```{r eval = TRUE, echo = FALSE, message = FALSE, fig.height = 5, fig.align = 'center'}
library(tidyverse)
summary <- read_csv("statistics/stats.csv") %>% 
  filter(target == 30)
summary
```
```{r eval = TRUE, echo = FALSE, message = FALSE, results = FALSE, fig.height = 4}
source("scripts/12d_Stat_fKappaCorrplot.R")
fKappaCorrplot(inpdir = "outputs/12_Stat/12e_Kappa/run5/",
  name_cols = c("SSP1-2.6", "SSP2-4.5", "SSP5-8.5", "Uninformed"))
```
