## Fisheries conservation features

The following were used in this study:

1. Distribution of selected bycatch species
2. Distribution of larval spawning grounds of selected commercially targeted species

### Bycatch distribution

First, we compiled a list of bycatch reported in the Pacific ABNJ. Then, we used the **IUCN** distribution maps for these species. These polygons are from the IUCN Red List, showing the known ranges of the species (IUCN Red List, 2021).

We limited the bycatch included in this study to **sea turtles**, but this workflow can be easily replicated and expanded to include more species.

The following were the sea turtles reported as bycatch and intersected with the study area:

* Loggerhead turtle (*Caretta caretta*)
* Green turtle (*Chelonia mydas*)
* Leatherback turtle (*Dermochelys coriacea*)
* Hawksbill turtle (*Eretmochelys imbricata*)
* Olive ridley turtle (*Lepidochelys olivacea*)

```{r, eval = TRUE, echo = FALSE, error = FALSE, warning = FALSE, message = FALSE, results = FALSE, fig.width=10, fig.height=7}
library(RColorBrewer)
library(patchwork)
world_sf <- readRDS("outputs/01_StudyArea/01a_StudyArea/PacificCenterLand.rds")
world_eez <- readRDS('outputs/01_StudyArea/01a_StudyArea/PacificCenterEEZ.rds')
Boundary = "EEZ"
world_eez <- cbind(world_eez,Boundary)

source("scripts/study_area/fCreateRobinsonBoundary.R")
Bndry <- fCreateRobinsonBoundary(west = 78, east = 140, north = 51, south = 60)

# calling data
loggerhead <- readRDS("outputs/03_IUCN/03b_fIUCNIntersect/Caretta_caretta_IUCN.rds")
green <- readRDS("outputs/03_IUCN/03b_fIUCNIntersect/Chelonia_mydas_IUCN.rds")
leatherback <- readRDS("outputs/03_IUCN/03b_fIUCNIntersect/Dermochelys_coriacea_IUCN.rds")
hawksbill <- readRDS("outputs/03_IUCN/03b_fIUCNIntersect/Eretmochelys_imbricata_IUCN.rds")
olive <- readRDS("outputs/03_IUCN/03b_fIUCNIntersect/Lepidochelys_olivacea_IUCN.rds")

loggerhead_plot <- ggplot() + 
                      geom_sf(data = loggerhead, fill = 'limegreen', size = 0.04, color = NA) + 
                      geom_sf(data = world_sf, fill = "grey20", colour = NA) +
                      coord_sf(xlim = c(st_bbox(Bndry)$xmin, st_bbox(Bndry)$xmax), 
                               ylim = c(st_bbox(Bndry)$ymin, st_bbox(Bndry)$ymax),
                               expand = TRUE) +
                      labs(title = "Loggerhead sea turtles") +
                      theme_bw()

green_plot <- ggplot() + 
                  geom_sf(data = green, fill = 'olivedrab', size = 0.04, color = NA) + 
                  geom_sf(data = world_sf, fill = "grey20", colour = NA) +
                  coord_sf(xlim = c(st_bbox(Bndry)$xmin, st_bbox(Bndry)$xmax), 
                           ylim = c(st_bbox(Bndry)$ymin, st_bbox(Bndry)$ymax),
                           expand = TRUE) +
                  labs(title = "Green sea turtles") +
                  theme_bw()

leatherback_plot <- ggplot() + 
                        geom_sf(data = leatherback, fill = 'darkseagreen', size = 0.04, color = NA) + 
                        geom_sf(data = world_sf, fill = "grey20", colour = NA) +
                        coord_sf(xlim = c(st_bbox(Bndry)$xmin, st_bbox(Bndry)$xmax), 
                                 ylim = c(st_bbox(Bndry)$ymin, st_bbox(Bndry)$ymax),
                                 expand = TRUE) +
                        labs(title = "Leatherback sea turtles") +
                        theme_bw()

hawksbill_plot <- ggplot() + 
                      geom_sf(data = hawksbill, fill = 'darkolivegreen3', size = 0.04, color = NA) + 
                      geom_sf(data = world_sf, fill = "grey20", colour = NA) +
                      coord_sf(xlim = c(st_bbox(Bndry)$xmin, st_bbox(Bndry)$xmax), 
                               ylim = c(st_bbox(Bndry)$ymin, st_bbox(Bndry)$ymax),
                               expand = TRUE) +
                      labs(title = "Hawksbill sea turtles") +
                      theme_bw()

olive_plot <- ggplot() + 
                geom_sf(data = olive, fill = 'springgreen1', size = 0.04, color = NA) + 
                geom_sf(data = world_sf, fill = "grey20", colour = NA) +
                coord_sf(xlim = c(st_bbox(Bndry)$xmin, st_bbox(Bndry)$xmax), 
                         ylim = c(st_bbox(Bndry)$ymin, st_bbox(Bndry)$ymax),
                         expand = TRUE) +
                labs(title = "Olive ridley sea turtles") +
                theme_bw()

iucn_turtle_plots <- (loggerhead_plot | green_plot | leatherback_plot) / (hawksbill_plot | olive_plot) +
  plot_annotation(tag_levels = "A",
                  tag_suffix = ")",
                  caption = "shapefiles from IUCN Red List (2021)")
iucn_turtle_plots
```

### Spawning grounds of commercially targeted species

Just like the bycatch layer, we compiled a list of commercially targeted large pelagic species managed in the Pacific from different sources. From this list, we have 4 species with available data on their global larval spawning grounds:

* Yellowfin Tuna (*Thunnus albacares*)
* Albacore (*Thunnus alalunga*)
* Skipjack Tuna (*Katsuwonus pelamis*)
* Swordfish (*Xiphias gladius*)

The models for these species are from a report by Mercer (2019) where he created Generalized Additive Models (GAMs) to predict spawning grounds using (Nishikawa et al., 1985). He used mean seasonal abundance from a historical dataset of plankton tows of fish larvae (dated back to the 1950s), and oceanographic and environmental conditions from global databases.

```{r, eval = TRUE, echo = FALSE, error = FALSE, warning = FALSE, message = FALSE, results = FALSE, fig.width=10, fig.height=7}
library(RColorBrewer)
library(patchwork)
pal_dist <- rev(brewer.pal(6, "Set3"))
world_sf <- readRDS("outputs/01_StudyArea/01a_StudyArea/PacificCenterLand.rds")

source("scripts/study_area/fCreateRobinsonBoundary.R")
Bndry <- fCreateRobinsonBoundary(west = 78, east = 140, north = 51, south = 60)

# calling data
PRED_global_YFT <- readRDS('outputs/04_commercial/04b_fCommercialFeat/YFT.rds')
PRED_global_ALB <- readRDS('outputs/04_commercial/04b_fCommercialFeat/ALB.rds')
PRED_global_SWO <- readRDS('outputs/04_commercial/04b_fCommercialFeat/SWO.rds')
PRED_global_SKP <- readRDS('outputs/04_commercial/04b_fCommercialFeat/SKP.rds')

# YFT
p1 <- ggplot()+
  geom_sf(data = PRED_global_YFT, fill = 'paleturquoise3', size = 0.04, color = NA) +
  geom_sf(data = world_sf, size = 0.05, fill = "grey20") +
  coord_sf(xlim = c(st_bbox(Bndry)$xmin, st_bbox(Bndry)$xmax), 
           ylim = c(st_bbox(Bndry)$ymin, st_bbox(Bndry)$ymax),
           expand = TRUE) +
  labs(title = "Yellow Tuna") +
  theme_bw()

# ALB
p2 <- ggplot()+
  geom_sf(data = PRED_global_ALB, fill = 'cornflowerblue', size = 0.04, color = NA) +
  geom_sf(data = world_sf, size = 0.05, fill = "grey20") +
  coord_sf(xlim = c(st_bbox(Bndry)$xmin, st_bbox(Bndry)$xmax), 
           ylim = c(st_bbox(Bndry)$ymin, st_bbox(Bndry)$ymax),
           expand = TRUE) +
  labs(title = "Albacore") +
  theme_bw()

# SKP
p3 <- ggplot()+
  geom_sf(data = PRED_global_SKP, fill = 'cadetblue4', size = 0.04, color = NA) +
  geom_sf(data = world_sf, size = 0.05, fill = "grey20") +
  coord_sf(xlim = c(st_bbox(Bndry)$xmin, st_bbox(Bndry)$xmax), 
           ylim = c(st_bbox(Bndry)$ymin, st_bbox(Bndry)$ymax),
           expand = TRUE) +
  labs(title = "Skipjack Tuna") +
  theme_bw()

# SWO
p4 <- ggplot()+
  geom_sf(data = PRED_global_SWO, fill = 'skyblue', size = 0.04, color = NA) +
  geom_sf(data = world_sf, size = 0.05, fill = "grey20") +
  coord_sf(xlim = c(st_bbox(Bndry)$xmin, st_bbox(Bndry)$xmax), 
           ylim = c(st_bbox(Bndry)$ymin, st_bbox(Bndry)$ymax),
           expand = TRUE) +
  labs(title = "Swordfish") +
  theme_bw()

global_plots <- (p1 + p2) / (p3 + p4) +
  plot_annotation(tag_levels = "A",
                  tag_suffix = ')',
                  caption = 'GAMs from Mercer (2019)')
global_plots

```
